---
title: "Title line"
author: "<br> Arthur Author <br> institution, department <br><br> Supervisors: Prof. Jane Doe,<br> Prof. Jack Smith<br>"
date: "ABC seminar <br> DD Mmmmm YYYY <br><br> _Slides -- [github.com/nspyrison/rmd_templates/slides_lite/](https://github.com/nspyrison/rmd_templates/slides_lite/)_"
output:
  xaringan::moon_reader:
    css: 
      - "assets/custom.css"
      - "assets/xaringan-themer.css"
    self_contained: false
    nature:
      ratio: '16:9'
      highlightStyle: github 
      highlightLanguage: r 
      highlightLines: true
      highlightSpans: false 
      countIncrementalSlides: false
      slideNumberFormat: '%current%/%total%'
      navigation:
        scroll: true 
        touch: true
        click: true
---
```{r setup_pres, include = FALSE}
knitr::opts_chunk$set(eval      = TRUE,   # R code 
                      echo      = FALSE,  # code text
                      include   = TRUE,   # plots
                      results   = 'asis', # text 'markup' 'asis' 'hold' 'hide'
                      fig.align = "center",
                      collapse  = TRUE,
                      message   = F, warning = F, error = F, 
                      cache     = F, cache.lazy = F
)
library(magrittr)
library(knitr)
library(kableExtra)
```

## Basics

- Use __---__ to create a new slide, 
    - Provided that it's followed by any level of __#__ header, which becomes the title of the slide.
- Bullets: top-level are made with `'- '`, the space is important.
    - Sub-level bullets need indentation of 4 spaces (2 tabs by default), _ie._ `'    - '`.

Use `--` to create an incremental slide break, hiding later content.
--

- `Xaringan` is very sensitive to white space, make sure to leave plenty of "breathing room"; an empty line before and after almost every bit of content.
- `Xaringan` is sensitive to comments; use `<!-- <comments> -->` sparingly!

--

Numbered lists with `N. content`:

1. item 1 
2. item 2

---

## Second slide

Can emphasize with quote blocks

> In the title slide; can use <br> to customize further!
--


high an r line by starting the line with an asterisk; _ie._ `* 3 + 4`

```{r eval=F, echo=T}
1 + 2
* 3 + 4
```

--
- Export to .pdf slides -- with `pagedown` and Chrome

```{r eval=F, echo=T}
## See: https://github.com/yihui/xaringan/wiki/Export-Slides-to-PDF
install.packages(c("pagedown", "xaringan"))
## Make sure you have pagedown >= 0.2 and xaringan >= 0.9; if not, run
pagedown::chrome_print("path/to/your/slides.rmd")

## Or just pass the HTML output file path to chrome_print()
pagedown::chrome_print("path/to/your/slides.html")
```


